Virtualization of a Real-Time Operating System for Robot Control with a Focus on Real-Time Compliance

### 2024-09-02 Masterarbeit_Robotik_Pamuk.tex
minor

\begin{table}[H]
	\centering
	\caption{Minimum, Average, and Maximum Latency with Overrun Counts of Bare Metal}
	\label{tab:latency_overrun_msw_hardware}
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		\textbf{Lat Min (µs)} & \textbf{Lat Avg (µs)} & \textbf{Lat Max (µs)} & \textbf{Overruns} \\ \hline
		0.613                 & 1.380                 & 10.709                & 0                 \\ \hline
	\end{tabular}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{img/implementation/gnuplot_combined_max_latency.png}
	\caption[Initial Comparison of Latency Distribution between Bare Metal and Virtualization]{Initial Comparison of Latency Distribution between Bare Metal and Virtualization}
	\label{fig:gnuplot_max_latency_combined}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{img/results/combined_latencies.png}
	\caption{Comparison of Robotic Application Latency of Salamander 4 after Configurations}
	\label{fig:combined_latencies}
\end{figure}

>>>>

\begin{table}[H]
	\centering
	\caption[Latency Statistics with Overrun Counts of Bare Metal]{Minimum, Average, and Maximum Latency with Overrun Counts of Bare Metal}
	\label{tab:latency_overrun_msw_hardware}
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		\textbf{Lat Min (µs)} & \textbf{Lat Avg (µs)} & \textbf{Lat Max (µs)} & \textbf{Overruns} \\ \hline
		0.613                 & 1.380                 & 10.709                & 0                 \\ \hline
	\end{tabular}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{img/implementation/gnuplot_combined_max_latency.png}
	\caption[Initial Comparison of Latency Distribution]{Initial Comparison of Latency Distribution between Bare Metal and Virtualization}
	\label{fig:gnuplot_max_latency_combined}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{img/results/combined_latencies.png}
	\caption{Comparison of Robotic Application Latency after Configurations}
	\label{fig:combined_latencies}
\end{figure}

### 2024-09-02 Paper.tex
minor

\begin{multicols}{2}
  \abstract{\textbf{This thesis investigates the virtualization of a real-time operating system, which is built with Yocto, employs hard real-time through Xenomai 3, and is emulated using QEMU/KVM. The primary objective was to bridge the latency gap between virtualized and bare metal versions to ensure deterministic and reliable behavior, which is crucial for real-time robotics. Initial latency measurements showed a high gap between bare metal and virtualized setups. Extensive tuning across BIOS, kernel, host OS, QEMU/KVM, and guest OS reduced the worst-case latency from 707.622~µs to 17.134~µs, close to the bare metal performance of 10.709~µs. The improvement was validated using a robotic application, comparing tuned virtualization with untuned and hardware versions.}} {\textbf{Virtualization, Real-Time Systems, Latency Reduction, Robot Control}}

>>>>

\begin{multicols}{2}
  \abstract{This thesis investigates the virtualization of a Real-Time Operating System (RTOS), which is built with Yocto, employs hard real-time through Xenomai 3, and is emulated using QEMU/KVM. The primary objective was to bridge the latency gap between virtualized and bare metal versions to ensure deterministic and reliable behavior, which is crucial for real-time robotics. Initial latency measurements showed a high gap between bare metal and virtualized setups. Extensive tuning across BIOS, kernel, host OS, QEMU/KVM, and guest OS reduced the worst-case latency from 707.622~µs to 17.134~µs, close to the bare metal performance of 10.709~µs. The improvement was validated using a robotic application, comparing tuned virtualization with untuned and hardware versions.} {Virtualization, Real-Time Systems, Latency Reduction, Robot Control}
